---
title: "Japan Export Import"
output: word_document
---

Upload the Files
```{r}
library(ggplot2)
library(readr)
library(plyr)
library(plotly)
library(dplyr)
library(tidyr)

country_df<-read.csv(file="E:/Capstone Project/japan dataset/New_dataset/japan-trade-statistics-1988-2016/country_eng.csv", header = TRUE, sep = ",")
head(country_df)

hs2_df<-read.csv(file = "E:/Capstone Project/japan dataset/New_dataset/japan-trade-statistics-1988-2016/hs2_eng.csv", header = TRUE, sep = "," )
head(hs2_df)

hs4_df<-read.csv(file = "E:/Capstone Project/japan dataset/New_dataset/japan-trade-statistics-1988-2016/hs4_eng.csv", header = TRUE,sep = ",")
head(hs4_df)

hs6_df<-read.csv(file = "E:/Capstone Project/japan dataset/New_dataset/japan-trade-statistics-1988-2016/hs6_eng.csv", header = TRUE,sep = ",")
head(hs6_df)

hs9_df<-read.csv(file = "E:/Capstone Project/japan dataset/New_dataset/japan-trade-statistics-1988-2016/hs9_eng.csv", header = TRUE,sep = ",")
head(hs9_df)

year_latest_df<-read.csv(file = "E:/Capstone Project/japan dataset/New_dataset/japan-trade-statistics-1988-2016/year_latest.csv", header = TRUE,sep = ",")
head(year_latest_df)

ym_latest_df<-read.csv(file = "E:/Capstone Project/japan dataset/New_dataset/japan-trade-statistics-1988-2016/ym_latest.csv", header = TRUE,sep = ",")
head(ym_latest_df)
```

```{r}
# Check if there is any null value in datasets
which(is.na(country_df))
which(is.na(hs2_df))
which(is.na(hs4_df))
which(is.na(hs6_df))
which(is.na(hs9_df))
which(is.na(year_latest_df))
which(is.na(ym_latest_df))
# there is no null values in datasets, so futher process merging the datasets.
```
There is no null values in datasets.

```{r}
## Merge the dataframes year and ym with country
year_country_df<-merge(country_df,year_latest_df,by="Country")
ym_country_df<-merge(country_df,ym_latest_df,by="Country")

## Variables transformation
## Create new month and derive exp_imp flg
ym_country_df$month_char<-month.abb[ym_country_df$month]
ym_country_df$month_char<-factor(ym_country_df$month_char, levels = month.abb)
head(ym_country_df)

addExportFlg<- function(datasets){
  datasets$type<-ifelse(datasets$exp_imp == 1, "Export", "Import")
  return(datasets)
}

smpl<-function(dataset){
  return(head(dataset,2))
}

year_country_df<-addExportFlg(year_country_df)
ym_country_df<-addExportFlg(ym_country_df)

## Drop some columns
drops<-c("exp_imp", "Country")
year_country_df<-year_country_df[ , !(names(year_country_df)%in% drops)]

drops<-c("exp_imp", "Country", "month")
ym_country_df<-ym_country_df[ , !(names(ym_country_df)%in% drops)]

rm(drops)
## Sample after Transfomation datasets
head(year_country_df,2)
summary(year_country_df)

head(ym_country_df,2)
summary(ym_country_df)

# Trade with each Area as Year wise
exp_summary_year_Export<-aggregate(as.numeric(year_country_df$VY),by=list(year_country_df$Year, year_country_df$type, year_country_df$Area),FUN = sum)
colnames(exp_summary_year_Export)<-c("Year","Type", "Area","Total.Values")

g1<-ggplot(exp_summary_year_Export, aes(x=Year, y= Total.Values ,color= Area))
g1 + geom_point() + facet_wrap(~Type,ncol = 2) + labs(title="Trade with each Area (Year wise)") + theme(plot.title=element_text(size = rel(1)))

# Trade with each Area as Month wise
exp_summary_ym_Import<-aggregate(as.numeric(ym_country_df$Year),by=list(ym_country_df$month ,ym_country_df$type, ym_country_df$Area),FUN = sum)
colnames(exp_summary_ym_Import)<-c("Month","Type", "Area","Total.Values")

g1<-ggplot(exp_summary_ym_Import, aes(x=Month, y= Total.Values ,color= Area))  
g1 + geom_point()+ facet_wrap(~Type, ncol = 2 ) + theme(axis.text.x = element_text(angle = 45,hjust = 1)) + labs(title="Trade with each Area as Month wise") + theme(plot.title=element_text(size = rel(1)))
```

Trade with each Areas
```{r}
# Joined trade records with country name
areas<-unique(country_df$Area)
head(areas)
grouped_by_area<-group_by(year_country_df,Year,Area)
vys<-aggregate(as.numeric(grouped_by_area$VY),by = list(grouped_by_area$Year,grouped_by_area$Area),FUN = sum)
colnames(vys)<-c("Year","Area","VY")

ggplot(vys,aes(x=Year,y=VY,color=Area)) + geom_line() + labs(title="Trade with each Areas") + theme(plot.title=element_text(size = rel(1)))
```
This graph shows Asia area is the biggest trade partner for Japan and the most growing partner. One thing to note here is that the VY is decreasing at 2008 for all areas. This trend was caused by "Bankruptcy of Lehman Brothers" which hit all around the world. And the VY value does not come back at the same level to before "Bankruptcy of Lehman Brothers" except for Asia area.
In addition there are two time span when trade value was decreased in the plot between Middle East. Japan depends on the oil imported from mainly Middle East. So the trend was caused by crude oil weaker trend recently. Let's confirm the main goods from Middle East.

```{r}
# Trade with Middle East Area
middle_east_countries<-filter(year_country_df,Area=="Middle_East")
head(middle_east_countries)
grouped_by_country<-group_by(middle_east_countries,Year,VY,Country_name)
vys<-aggregate(as.numeric(grouped_by_country$VY),by = list(grouped_by_country$Year,grouped_by_country$Country_name),FUN = sum)
colnames(vys)<-c("Year","Country_name","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
gp<-ggplot(vys,aes(x=Year,y=VY,color=Country_name)) + geom_line() 
gp + facet_wrap(~Country_name,ncol=2) + labs(title="Trade with Middle East Countries") + theme(plot.title=element_text(size = rel(1)))

# Trade of different products b/w Middle east-Japan
middle_hs2_df<-filter(year_country_df,Area=="Middle_East")
head(middle_hs2_df)
summary(middle_hs2_df)
grouped_by_hs2<-group_by(middle_hs2_df,hs2,Year,VY)

# Summarize data
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$Country_name,grouped_by_hs2$hs2),FUN=sum)
colnames(vys)<-c("Year","Country_name","hs2","VY")

# Merge vys with hs2_df
vys<-merge(vys,hs2_df,by = "hs2")
vys$percent<-prop.table(vys$VY)
head(vys)
main_goods<-filter(vys,VY >= 0.6)
hs2_names<-unique(main_goods,main_goods$hs2_name,incomparables = FALSE)
ggplot(hs2_names,aes(x=hs2_name,y=VY)) + geom_bar(stat = "identity",fill="red",width = 0.8) + coord_flip() + labs(title="Trade of different products with Middle East")
# Another way
ggplot(hs2_names,aes(x=Year,y=VY,color=Country_name)) + geom_line() + facet_wrap(~hs2_name,ncol = 5) + labs(title="Trade of different products with Middle East's Countries")

#Merge hs2 with year_country_df
year_hs2_country<-merge(year_country_df,hs2_df,by="hs2")
# Trade with different Industrial products b/w Iran-Japan
iran_df<-filter(year_hs2_country,Country_name == "Iran")
head(iran_df)
ggplot(iran_df,aes(x=Year,y=VY,fill=type)) + geom_bar(stat = "identity") + labs(title="Export Import b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1)))
grouped_by_hs2<-group_by(iran_df,Year,VY,hs2,hs2_name)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2,grouped_by_hs2$hs2_name),FUN=sum)
colnames(vys)<-c("Year","hs2","hs2_name","VY")
main_goods<-filter(vys,hs2 == c("27","30","39","40","44","70","72","84","85","86","87","88","89","93") )
main_goods$percent<-prop.table(main_goods$VY)
head(main_goods)
# Visualisation View
gp<-ggplot(main_goods,aes(x=hs2_name,y=VY,fill=hs2_name)) + geom_bar(stat = "identity",fill="red",width = 0.8) + labs(title="Trade of different Industrial products b/w Iran-Japan")
gp + coord_flip() + theme(plot.title=element_text(size = rel(1))) 
```
We can see several goods are traded between Japan and Middle East areas. As expected the most traded goods after 2010 is "Mineral Fuels". "Mineral Fuels" is the only good which trade was decreased from 2014's.
```{r}
## Export Import auto mobile(car) b/w Iran-Japan 
iran_hs2_df<-filter(year_hs2_country,hs2 == "87")
head(iran_hs2_df)
grouped_by_df<-group_by(iran_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_df$VY),by=list(grouped_by_df$Year,grouped_by_df$hs2_name,grouped_by_df$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visulization View 
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of auto_mobile(car) b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Export Import of Mineral Fuels b/w Iran-Japan
iran_hs2_df<-filter(year_hs2_country,hs2 == "27" )
head(iran_hs2_df)
grouped_by_df<-group_by(iran_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_df$VY),by=list(grouped_by_df$Year,grouped_by_df$hs2_name,grouped_by_df$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visulization View 
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Mineral fuels b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Export Import of Machines b/w Iran-Japan
iran_hs2_df<-filter(year_hs2_country,hs2 == "84")
head(iran_hs2_df)
grouped_by_df<-group_by(iran_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_df$VY),by=list(grouped_by_df$Year,grouped_by_df$hs2_name,grouped_by_df$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visulization View 
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Machines b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# export import of Electrical machinery b/w Iran-Japan
iran_hs2_df<-filter(year_hs2_country,hs2 == "85")
head(iran_hs2_df)
grouped_by_df<-group_by(iran_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_df$VY),by=list(grouped_by_df$Year,grouped_by_df$hs2_name,grouped_by_df$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visulization View 
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Electrical Machinery b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade of Iron and Steel b/w Iran-Japan
iran_hs2_df<-filter(year_hs2_country,hs2 == "72")
head(iran_hs2_df)
grouped_by_hs2<-group_by(iran_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visualisation View
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Iron and Steel b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Merge hs4 with year_country_df
year_hs4_country<-merge(year_country_df,hs4_df,by="hs4")
# Trade of different kinds of Crops b/w Iran-Japan
iran_hs4_df<-filter(year_hs4_country,Country_name == "Iran")
head(iran_hs4_df)
grouped_by_hs4<-group_by(iran_hs4_df,Year,VY,hs4,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
main_crops<-filter(vys,hs4 == c("1004","1005","1006","1007","1101","1102"))
main_crops$percent<-prop.table(main_crops$VY)
head(main_crops)
# Visualisation View
ggplot(main_crops,aes(x=hs4_name,y=VY,fill =type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of different kinds of Crops b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1))) 
```

```{r}
# Trade of different kinds of Vegetables b/w Iran-Japan
iran_hs4_df<-filter(year_hs4_country,Country_name == "Iran")
head(iran_hs4_df)
grouped_by_hs4<-group_by(iran_hs4_df,Year,VY,hs4,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
main_veges<-filter(vys,hs4 == c(701:710))
main_veges$percent<-prop.table(main_veges$VY)
head(main_veges)
# Visualisation View
ggplot(main_veges,aes(x=hs4_name,y=VY))  + geom_bar(stat="identity", position = "dodge",fill="red",width = 0.8) + labs(title="Export Import of different kinds of Crops b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1))) + coord_flip()

# Export Import of Leguminous Vegetables b/w Iran-Japan
main_vege<-filter(vys,hs4 == "708")
main_vege$percent<-prop.table(main_vege$VY)
head(main_vege)
ggplot(main_vege,aes(x=Year,y=VY,fill = type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Leguminous Vegetables b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade of different Fruits b/w Iran-Japan
iran_hs4_df<-filter(year_hs4_country,Country_name == "Iran")
head(iran_hs4_df)
grouped_by_hs4<-group_by(iran_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
main_fruits<-filter(vys,hs4 == c("803","805","806","807","808","810"))
main_fruits$percent<-prop.table(main_fruits$VY)
head(main_fruits)
ggplot(main_fruits,aes(x=hs4_name,y=VY)) + geom_bar(stat="identity", position = "dodge",fill="red",width = 0.8) + labs(title="Trade of different fruits b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1))) + coord_flip()

# Export and Import of Grapes b/w Iran-Japan
main_fruits<-filter(vys,hs4 == "806")
main_fruits$percent<-prop.table(main_fruits$VY)
head(main_fruits)
ggplot(main_fruits,aes(x=Year,y=VY,fill = type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Grapes b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1))) 

# Export and Import of Melons b/w Iran-Japan
main_fruits<-filter(vys,hs4 == "807")
main_fruits$percent<-prop.table(main_fruits$VY)
head(main_fruits)
ggplot(main_fruits,aes(x=Year,y=VY,fill = type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Melons b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1))) 

# Export and Import of Other Fruits b/w Iran-Japan
main_fruits<-filter(vys,hs4 == "810")
main_fruits$percent<-prop.table(main_fruits$VY)
head(main_fruits)
ggplot(main_fruits,aes(x=Year,y=VY,fill = type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Other Fruits b/w Iran-Japan") + theme(plot.title=element_text(size = rel(1))) 
```


```{r}
# Trade of different Oils b/w Iran-Japan
middle_hs4_df<-filter(year_hs4_country,Country_name == "Saudi_Arabia")
head(middle_hs4_df)
grouped_by_hs4<-group_by(middle_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
main_oils<-filter(vys,hs4 == c("1507","1508","1509","1510","1511"))
main_oils$percent<-prop.table(main_oils$VY)
head(main_oils)
ggplot(main_oils,aes(x=hs4_name,y=VY)) + geom_bar(stat="identity", position = "dodge",fill="red",width = 0.8) + labs(title="Trade of different kinds of Oils b/w Saudi_Arabia-Japan") + theme(plot.title=element_text(size = rel(1))) + coord_flip()
```


```{r, echo=TRUE}
areas<-unique(country_df$Area)
grouped_by_area<-group_by(year_country_df,Year,Area)
vys<-aggregate(as.numeric(grouped_by_area$VY),by = list(grouped_by_area$Year,grouped_by_area$Area),FUN = sum)
colnames(vys)<-c("Year","Area","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
bp<-ggplot(vys,aes(x=Area,y=VY)) + geom_boxplot(aes(fill=Area)) 
bp + theme(axis.text.x = element_text(angle = 45,hjust = 1)) + scale_fill_brewer(palette = "PRGn")
```
We can see the trade growth (the difference between mean value and high deviation) of Asia area is the most. On the other hand the trade between Japan and North America or Western Europe relatively stable though they are ranked as 2nd and 3rd position. The growth of Middle East is relatively high compared with North America and Western Europe.

Trade with Asian countries
```{r}
#Trade with Asian countries
asian_countries<-filter(year_country_df,Area=="Asia")
head(asian_countries) 
summary(asian_countries)
grouped_by_country<-group_by(asian_countries,Year,VY,Country_name)
vys<-aggregate(as.numeric(grouped_by_country$VY),by = list(grouped_by_country$Year,grouped_by_country$Country_name),FUN = sum)
colnames(vys)<-c("Year","Country_name","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
gp<-ggplot(vys,aes(x=Year,y=VY,color=Country_name)) + geom_line() 
gp + facet_wrap(~Country_name,ncol=4) + labs(title="Trade with Asian Countries") + theme(plot.title=element_text(size = rel(1)))

# Trade of hs2 with Asian Countries
asian_hs2_df<-filter(year_hs2_country,Area=="Asia")
which(is.na(asian_hs2_df))
grouped_by_hs2<-group_by(asian_hs2_df,Year,VY,hs2_name,Country_name)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$Country_name),FUN=sum)
colnames(vys)<-c("Year","hs2_name","Country_name","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
main_goods<-filter(vys,VY>=0.4 )
head(main_goods)
hs2_names<-unique(main_goods,main_goods$hs2_name,incomparables = FALSE)
for(hs2_name in hs2_names){
  plot(hs2_names$Year,hs2_names$hs2_name,xlab = "Year",ylab = "hs2_name")
}
ggplot(hs2_names,aes(x=hs2_name,y=VY)) + geom_bar(stat = "identity",fill="red") + coord_flip() + labs(title="Trade of different products with Asian Countries")
# Another Visualisation
ggplot(hs2_names,aes(x=Year,y=VY,color=Country_name)) + geom_line() + facet_wrap(~hs2_name,ncol=5) + labs(title="Trade of different products with Asian Countries")
```

Trade with China
```{r}
# Trade with different Industrial products b/w China-Japan
china_df<-filter(year_hs2_country,Country_name == "People's_Republic_of_China")
head(china_df)
summary(china_df)
ggplot(china_df,aes(x=Year,y=VY,fill =type)) + geom_bar(stat = "identity") + labs(title="Export Import b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
grouped_by_hs2<-group_by(china_df,Year,VY,hs2,hs2_name)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2,grouped_by_hs2$hs2_name),FUN=sum)
colnames(vys)<-c("Year","hs2","hs2_name","VY")
main_goods<-filter(vys,hs2 == c("27","30","39","40","44","70","72","84","85","86","87","88","89","93") )
main_goods$percent<-prop.table(main_goods$VY)
head(main_goods)
# Visualisation View
gp<-ggplot(main_goods,aes(x=hs2_name,y=VY,fill=hs2_name)) + geom_bar(stat = "identity",fill="red",width = 0.8) + labs(title="Trade of different Industrial products b/w China-Japan")
gp + coord_flip() + theme(plot.title=element_text(size = rel(1))) 
```

```{r}
# Minor goods trade by China
minor_goods<-filter(vys,VY < 0.1*1e6 )
minor_goods$percent<-prop.table(minor_goods$VY)
head(minor_goods)
hs2_names<-unique(minor_goods,minor_goods$hs2_name,incomparables = FALSE)

gp<-ggplot(hs2_names,aes(x=hs2_name,y=VY,fill=hs2_name)) + geom_bar(stat = "identity",position = "dodge",fill="red",width = 0.8) + labs(title="Trade of different products with China")
gp + theme(plot.title=element_text(size = rel(1))) + coord_flip()
```
Here we can see that Aircraft and cork are not changing so much.
##Conclusion
We can see some interesting points from these data set.
The trade value was decreased at 2008 all over the world.
The main goods traded between Japan and Middle East is oil.
The trade value of crude oil was decreasing recently due to low price of oil.
China is the biggest trade partner for Japan.

```{r}
# Trade of Plastics and articles product b/w China & Japan
china_hs2_df<-filter(year_hs2_country,hs2 == "39")
head(china_hs2_df)
grouped_by_hs2<-group_by(china_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visualisation View
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Plastics and articles b/w China & Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade of Rubber and articles product b/w China & Japan
china_hs2_df<-filter(year_hs2_country,hs2 == "40")
head(china_hs2_df)
grouped_by_hs2<-group_by(china_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visualisation View
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Rubber and articles b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade of Wood and articles product b/w China & Japan
china_hs2_df<-filter(year_hs2_country,hs2 == "44")
head(china_hs2_df)
grouped_by_hs2<-group_by(china_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visualisation View
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Wood and articles b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade of Iron and Steel product b/w China-Japan
china_hs2_df<-filter(year_hs2_country,hs2 == "72")
head(china_hs2_df)
grouped_by_hs2<-group_by(china_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visualisation View
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Iron and Steel b/w China & Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade of auto_mobile(car) b/w China & Japan
china_hs2_df<-filter(year_hs2_country,hs2 == "87")
head(china_hs2_df)
grouped_by_hs2<-group_by(china_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visualisation View
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of auto_mobile(car) b/w China & Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Export import of Electrical Machinery b/w China-Japan
china_hs2_df<-filter(year_hs2_country,hs2 == "85")
head(china_hs2_df)
grouped_by_hs2<-group_by(china_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visualisation View
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Electrical Machinery b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Export import of Machines b/w China-Japan
china_hs2_df<-filter(year_hs2_country,hs2 == "84")
head(china_hs2_df)
grouped_by_hs2<-group_by(china_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visualisation View
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Machines b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Export import of Aircrafts b/w China-Japan
china_hs2_df<-filter(year_hs2_country,hs2 == "88")
head(china_hs2_df)
grouped_by_hs2<-group_by(china_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visualisation View
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Aircrafts b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
#merge hs4 with year_country_df
year_hs4_country<-merge(year_country_df,hs4_df,by="hs4")
# Trade of different Crops b/w China-Japan
china_hs4_df<-filter(year_hs4_country,Country_name == "People's_Republic_of_China")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
main_crops<-filter(vys,hs4 == c("1004","1005","1006","1007","1101","1102"))
main_crops$percent<-prop.table(main_crops$VY)
head(main_crops)
ggplot(main_crops,aes(x=hs4_name,y=VY)) + geom_bar(stat="identity", position = "dodge",fill="red",width = 0.8) + labs(title="Trade of different crops b/w China-Japan") + theme(plot.title=element_text(size = rel(1))) + coord_flip()
```

```{r}
# Trade of Maize(corn) b/w China-Japan
china_hs4_df<-filter(year_hs4_country,hs4 == "1005")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
ggplot(vys,aes(x=Year,y=VY,fill=type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Maize(corn) b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade of Rice b/w China-Japan
china_hs4_df<-filter(year_hs4_country,hs4 == "1006")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
ggplot(vys,aes(x=Year,y=VY,fill=type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Rice b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade of Wheat b/w China-Japan
china_hs4_df<-filter(year_hs4_country,hs4 == "1101")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
ggplot(vys,aes(x=Year,y=VY,fill=type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Wheat b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade of different Vegetables b/w China-Japan
china_hs4_df<-filter(year_hs4_country,Country_name == "People's_Republic_of_China")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
main_veges<-filter(vys,hs4 == c(701:710))
main_veges$percent<-prop.table(main_veges$VY)
head(main_veges)
ggplot(main_veges,aes(x=hs4_name,y=VY)) + geom_bar(stat="identity", position = "dodge",fill="red",width = 0.8) + labs(title="Trade of different Vegetables b/w China-Japan") + theme(plot.title=element_text(size = rel(1))) + coord_flip()
```

```{r}
# Export import of Frozen vegetables b/w china-Japan
china_hs4_df<-filter(year_hs4_country,hs4 == "710")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
ggplot(vys,aes(x=Year,y=VY,fill=type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Frozen Vegetables b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Export import of Onions b/w China-Japan
china_hs4_df<-filter(year_hs4_country,hs4 == "703")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
ggplot(vys,aes(x=Year,y=VY,fill=type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Onions b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Export import of Other vegetables b/w China-Japan
china_hs4_df<-filter(year_hs4_country,hs4 == "709")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
ggplot(vys,aes(x=Year,y=VY,fill=type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Other Vegetables b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade of different Fruits b/w China-Japan
china_hs4_df<-filter(year_hs4_country,Country_name == "People's_Republic_of_China")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
main_fruits<-filter(vys,hs4 == c("803","805","806","807","808","810"))
main_fruits$percent<-prop.table(main_fruits$VY)
head(main_fruits)
ggplot(main_fruits,aes(x=hs4_name,y=VY)) + geom_bar(stat="identity", position = "dodge",fill="red",width = 0.8) + labs(title="Trade of different fruits b/w China-Japan") + theme(plot.title=element_text(size = rel(1))) + coord_flip()
```

```{r}
# Export import of Bananas b/w China-Japan
china_hs4_df<-filter(year_hs4_country,hs4 == "803")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
ggplot(vys,aes(x=Year,y=VY,fill = type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Bananas b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Export import of Grapes b/w China-Japan
china_hs4_df<-filter(year_hs4_country,hs4 == "806")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
ggplot(vys,aes(x=Year,y=VY,fill= type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Grapes b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Export import of Apples b/w China-Japan
china_hs4_df<-filter(year_hs4_country,hs4 == "808")
head(china_hs4_df)
grouped_by_hs4<-group_by(china_hs4_df,Year,VY,hs4_name,type)
vys<-aggregate(as.numeric(grouped_by_hs4$VY),by=list(grouped_by_hs4$Year,grouped_by_hs4$hs4,grouped_by_hs4$hs4_name,grouped_by_hs4$type),FUN=sum)
colnames(vys)<-c("Year","hs4","hs4_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
ggplot(vys,aes(x=Year,y=VY,fill= type)) + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Apples b/w China-Japan") + theme(plot.title=element_text(size = rel(1)))
```


```{r}
#merge hs6 with year_country_df
year_hs6_country<-merge(year_country_df,hs6_df,by="hs6")
china_hs6_df<-filter(year_hs6_country,Country_name == "People's_Republic_of_China")
head(china_hs6_df)
grouped_by_hs6<-group_by(china_hs6_df,Year,VY,hs6_name,type)
vys<-aggregate(as.numeric(grouped_by_hs6$VY),by=list(grouped_by_hs6$Year,grouped_by_hs6$hs6,grouped_by_hs6$hs6_name,grouped_by_hs6$type),FUN=sum)
colnames(vys)<-c("Year","hs6","hs6_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
main_goods<-filter(vys,hs6 == c("160411","110423","120991","150810","200570"))
head(main_goods)
# Visualisation View
ggplot(main_goods,aes(x=Year,y=VY,color=hs6_name))  + geom_line() + labs(title="Export Import hs6 from China") + theme(plot.title=element_text(size = rel(2)))
main_goods<-filter(vys,hs6 == "160411")
ggplot(main_goods,aes(x=Year,y=VY,fill=type))  + geom_bar(stat = "Identity") + labs(title="Export Import Salmon from China") + theme(plot.title=element_text(size = rel(1)))
```

```{r}
# Trade with different Industrial products b/w Iran-Japan
iran_df<-filter(year_hs2_country,Country_name == "Iran")
head(iran_df)
grouped_by_hs2<-group_by(iran_df,Year,VY,hs2,hs2_name)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2,grouped_by_hs2$hs2_name),FUN=sum)
colnames(vys)<-c("Year","hs2","hs2_name","VY")
main_goods<-filter(vys,hs2 == c("27","30","39","40","44","70","72","84","85","86","87","88","89","93") )
main_goods$percent<-prop.table(main_goods$VY)
head(main_goods)
# Visualisation View
gp<-ggplot(main_goods,aes(x=hs2_name,y=VY,fill=hs2_name)) + geom_bar(stat = "identity",fill="red",width = 0.8) + labs(title="Trade of different Industrial products b/w Iran-Japan")
gp + coord_flip() + theme(plot.title=element_text(size = rel(1))) 
```

```{r}
# Trade of Rubber and articles product b/w China & Japan
iran_df<-filter(year_hs2_country,hs2 == "")
head(iran_hs2_df)
grouped_by_hs2<-group_by(china_hs2_df,Year,VY,hs2_name,type)
vys<-aggregate(as.numeric(grouped_by_hs2$VY),by=list(grouped_by_hs2$Year,grouped_by_hs2$hs2_name,grouped_by_hs2$type),FUN=sum)
colnames(vys)<-c("Year","hs2_name","type","VY")
vys$percent<-prop.table(vys$VY)
head(vys)
# Visualisation View
ggplot(vys,aes(x=Year,y=VY,fill=type))  + geom_bar(stat="identity", position = "dodge") + labs(title="Export Import of Plastics and articles b/w China & Japan") + theme(plot.title=element_text(size = rel(1)))
```

